---
title: "lg"
author: "Tingting"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggforce)
library(pheatmap)
library(RColorBrewer)
library(vegan)
library(broom)
library(ggstance)
library(lubridate)
library(readxl)
library(ggpubr)
library(janitor)
library(rio)
library(tidyr)
library(caret)
library(mlbench)
library(doMC)
library(caret)
library(pROC)
library(mixOmics)
library(tidyverse)
library(mixOmicsCaret)  
library(mlbench)
library(ggplot2)
library(forcats)
library(dplyr)
library(openxlsx)
```

## R Markdown

```{r cars}
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/copsac/Data/ksads/covariat_all_18.Rdata")
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/copsac/Data/ksads/diag_all_name.Rdata")

all_annotation<-read.xlsx("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/copsac/Data/CORI-01-23PHML/CORI-01-23PHML_new/Chemical_Annotation_Common.xlsx")
# Add "X" to the start of each cell in the specific column
all_annotation$CHEM_ID <- paste("X", all_annotation$CHEM_ID, sep = "")

longti_data<-read.xlsx("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/copsac/Data/CORI-01-23PHML/CORI-01-23PHML_new/all_anchor_norm_impute30_log_output.xlsx")
names(longti_data)[4:791] <- paste("X", names(longti_data)[4:791], sep = "")
longti_data<-na.omit(longti_data)
longti_data_1<-longti_data%>%filter(TP%in% c("Mor_w24","Mor_w1","6mth", "18mth", "6yr","10yr"))

longti_data_2 <- longti_data_1[, !grepl("^X9999", names(longti_data_1))]



filtered_df_diag0<-left_join(diag_all_name[,c(1,3,5,8)],longti_data_2, by="ABCNO")
filtered_df_diag0<-na.omit(filtered_df_diag0)


w24<-filtered_df_diag0%>%filter(TP=="Mor_w24")
w1<-filtered_df_diag0%>%filter(TP=="Mor_w1")
mth6<-filtered_df_diag0%>%filter(TP=="6mth")
mth6<-mth6[!duplicated(mth6$ABCNO), ]
mth18<-filtered_df_diag0%>%filter(TP=="18mth")
yr6<-filtered_df_diag0%>%filter(TP=="6yr")
yr6<-yr6[!duplicated(yr6$ABCNO), ]
yr10<-filtered_df_diag0%>%filter(TP=="10yr")
yr10<-yr10[!duplicated(yr10$ABCNO), ]

names(w24)

w24_1<-w24[,c(4,7:690)]
mth6_1<-mth6[,c(4,7:690)]
mth18_1<-mth18[,c(4,7:690)]
yr6_1<-yr6[,c(4,7:690)]
yr10_1<-yr10[,c(4,7:690)]
w1_1<-w1[,c(4,7:690)]

load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/bmi/BMI18mth.Rdata")
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/bmi/BMI6mth.Rdata")
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/bmi/BMI6yr.Rdata")
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/bmi/BMI10yr.Rdata")
load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/bmi/BMI_overweight_6mth_10yr.Rdata")
Birth<- import('/Volumes/Data/COPSAC-2010/Birth/ABC0016_Delivery.xlsx',sheet=3) %>% 
  clean_names() 
Birth<-Birth%>%
  mutate(Birth_way = case_when(Birth$delivery %in% c("Normal") ~ "0",
                           Birth$delivery %in% c("Planned sectio", "Acute sectio") ~ "1"))%>% dplyr::select(abcno, Birth_way)
colnames(Birth)[1]<-"ABCNO"
colnames(BMI18mth)[1]<-"ABCNO"
colnames(BMI6mth)[1]<-"ABCNO"
colnames(BMI6yr)[1]<-"ABCNO"
colnames(BMI10yr)[1]<-"ABCNO"

load("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/copsac/Data/ksads/psychopathology_wide.Rdata")

psychopathology_wide_s<-data.frame(psychopathology_wide)[,c(1:7,9,13:17,50,51,56)]
#psychopathology_wide_s<-data.frame(psychopathology_wide)[,c(1:7,9,13:17,50,51,56)]
psychopathology_wide_s[,c(1,4,7,8,11,16)]
names(psychopathology_wide_s)
colnames(psychopathology_wide_s)[1]<-"ABCNO"

n_w24<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),w24[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")
n_18m<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),BMI18mth%>%dplyr::select(1,2),mth18[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")
n_6m<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),BMI6mth%>%dplyr::select(1,2),mth6[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")
n_6yr<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),BMI6yr%>%dplyr::select(1,2),yr6[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")
n_10yr<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),BMI10yr%>%dplyr::select(1,2),yr10[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")
n_w1<-list(covariat_all_18%>%dplyr::select(1),psychopathology_wide_s[,c(1,3,5,11,16)],covariat_all_18%>%dplyr::select(1,5:18),Birth,w1[,c(1,7:690)])%>%reduce(left_join,by="ABCNO")

```
w24 adhdrs_adhd_symptoms_sc_f
```{r}
#W24
hold_w24<-n_w24
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 20:length(names(hold_w24)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_w24)[i],"+ sex+
                             motherage + mother_smoking +ab_preg_yn + preeclampsia3rdtrimester +mother_bmi +ga +birthweight +familyincome_at1week +maternal_education_at1w+ paternal_education_at1w+alcohol_all+diabetes_all" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w24)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w24)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_w24<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_adhdrs_w24,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_w24_adj_4scores.csv")

Result_table_Significant_adhdrs_w24 <- subset(Result_table_fdr_adhdrs_w24,p.value<= 0.05)#62 significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))


#merge_table<- left_join(Result_table_Significant_log, pathway 
 #                       %>% select(Metabolites, Super_pathway,CHEMICAL_NAME), by ="Metabolites")

Result_table_Significant_adhdrs_w24<-Result_table_Significant_adhdrs_w24[with(Result_table_Significant_adhdrs_w24,order(FDR)),]

#######plot the data
plot_adhdrs_w24_adj <- Result_table_Significant_adhdrs_w24 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "OR", title = "W24_ADHD-RS-adjusted (60)",
    color = "Pathway"
  )

plot_adhdrs_w24_adj
```
W24-ASD_TOT_P
```{r}
#W24
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 20:length(names(hold_w24)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_w24)[i],"+ sex+
                             motherage + mother_smoking +ab_preg_yn + preeclampsia3rdtrimester +mother_bmi +ga +birthweight +familyincome_at1week +maternal_education_at1w+ paternal_education_at1w+alcohol_all+diabetes_all" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,na.action=na.omit, data=hold_w24)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w24)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_w24<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_w24,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_w24_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_w24 <- subset(Result_table_fdr_ADHD_TOT_P_MCA1_w24,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_ADHD_TOT_P_MCA1_w24<-Result_table_Significant_ADHD_TOT_P_MCA1_w24[with(Result_table_Significant_ADHD_TOT_P_MCA1_w24,order(FDR)),]

#######plot the data
plot_ADHD_TOT_P_MCA1_w24_adj <- Result_table_Significant_ADHD_TOT_P_MCA1_w24 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "OR", title = "W24_ADHD_TOT_P_MCA1-adjusted (60)",
    color = "Pathway"
  )

plot_ASD_TOT_P_w24_adj

```

W24 ATT_TOT_P
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 20:length(names(hold_w24)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_w24)[i],"+ sex+
                             motherage + mother_smoking +ab_preg_yn + preeclampsia3rdtrimester +mother_bmi +ga +birthweight +familyincome_at1week +maternal_education_at1w+ paternal_education_at1w+alcohol_all+diabetes_all" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w24)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w24)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_w24<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ASD_TOT_P_MCA1_w24,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_w24_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_w24 <- subset(Result_table_fdr_ASD_TOT_P_MCA1_w24,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_ASD_TOT_P_MCA1_w24<-Result_table_Significant_ASD_TOT_P_MCA1_w24[with(Result_table_Significant_ASD_TOT_P_MCA1_w24,order(FDR)),]

#######plot the data
plot_ASD_TOT_P_MCA1_w24_adj <- Result_table_Significant_ATT_TOT_P_w24 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "OR", title = "W24_ASD_TOT_P_MCA1-adjusted (49)",
    color = "Pathway"
  )

plot_ASD_TOT_P_MCA1_w24_adj
```

W24 SRS-2
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 20:length(names(hold_w24)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_w24)[i],"+ sex+
                             motherage + mother_smoking +ab_preg_yn + preeclampsia3rdtrimester +mother_bmi +ga +birthweight +familyincome_at1week +maternal_education_at1w+ paternal_education_at1w+alcohol_all+diabetes_all" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,na.action=na.omit, data=hold_w24)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w24)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_w24<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_total_srs2_srr_w24,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_w24_adj.csv")

Result_table_Significant_total_srs2_srr_w24 <- subset(Result_table_fdr_total_srs2_srr_w24,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_total_srs2_srr_w24<-Result_table_Significant_total_srs2_srr_w24[with(Result_table_Significant_total_srs2_srr_w24,order(FDR)),]

#######plot the data
plot_total_srs2_srr_w24_adj <- Result_table_Significant_total_srs2_srr_w24 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "OR", title = "W24_total_srs2_srr-adjusted (33)",
    color = "Pathway"
  )

plot_total_srs2_srr_w24_adj
```

w1
```{r}
hold_w1<-n_w1
names(hold_w1)

Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_w1)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_w1)[i],"+ sex+
                             motherage  +mother_bmi +ga+ mother_smoking +maternal_education_at1w+paternal_education_at1w+familyincome_at1week+ab_preg_yn +diabetes_all+Birth_way" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w1)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w1)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################unadjusted

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_w1<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ASD_TOT_P_MCA1_w1,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_w1_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_w1 <- subset(Result_table_fdr_ASD_TOT_P_MCA1_w1,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_ASD_TOT_P_MCA1_w1<-Result_table_Significant_ASD_TOT_P_MCA1_w1[with(Result_table_Significant_ASD_TOT_P_MCA1_w1,order(FDR)),]

#######plot the data
plot_ASD_TOT_P_MCA1_w1_adj <- Result_table_Significant_ASD_TOT_P_MCA1_w1 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "W1_ASD_TOT_P-adjusted",
    color = "Pathway"
  )

plot_ASD_TOT_P_w1_adj
```
WEEK 1 adj
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_w1)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_w1)[i],"+ sex+
                             motherage  +mother_bmi +ga+ mother_smoking +maternal_education_at1w+paternal_education_at1w+familyincome_at1week+ab_preg_yn +diabetes_all+Birth_way" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w1)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w1)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################unadjusted

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_w1<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_w1,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_w1_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_w1 <- subset(Result_table_fdr_ADHD_TOT_P_MCA1_w1,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_ADHD_TOT_P_MCA1_w1<-Result_table_Significant_ADHD_TOT_P_MCA1_w1[with(Result_table_Significant_ADHD_TOT_P_MCA1_w1,order(FDR)),]

#######plot the data
plot_ADHD_TOT_P_MCA1_w1_adj <- Result_table_Significant_ADHD_TOT_P_MCA1_w1 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "W1_ADHD_TOT_P-adjusted",
    color = "Pathway"
  )

plot_ATT_TOT_P_w1_adj
```
W1 ASD

w1 adhdrs_adhd_symptoms_sc_f
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_w1)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_w1)[i],"+ sex+
                             motherage  +mother_bmi +ga+ mother_smoking +maternal_education_at1w+paternal_education_at1w+familyincome_at1week+ab_preg_yn +diabetes_all+Birth_way" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w1)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w1)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################unadjusted

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_w1<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_adhdrs_w1,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_w1_adj.csv")

Result_table_Significant_adhdrs_w1 <- subset(Result_table_fdr_adhdrs_w1,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_adhdrs_w1<-Result_table_Significant_adhdrs_w1[with(Result_table_Significant_adhdrs_w1,order(FDR)),]

#######plot the data
plot_adhdrs_w1_adj <- Result_table_Significant_adhdrs_w1 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "W1_adhdrs-adjusted",
    color = "Pathway"
  )

plot_adhdrs_w1_adj
```
w1 total_srs2_srr
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_w1)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_w1)[i],"+ sex+
                             motherage  +mother_bmi +ga+ mother_smoking +maternal_education_at1w+paternal_education_at1w+familyincome_at1week+ab_preg_yn +diabetes_all+Birth_way" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_w1)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_w1)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################unadjusted

################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_w1<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_total_srs2_srr_w1,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_w1_adj.csv")

Result_table_Significant_total_srs2_srr_w1 <- subset(Result_table_fdr_total_srs2_srr_w1,p.value<= 0.05)#49significant
#logtransform <- function(x, na.rm = FALSE) (x %>% log())
#Result_table_Significant_adhdrs_w24_log <- Result_table_Significant_adhdrs_w24 %>% mutate(across(c("OR":"CIH"), logtransform))

Result_table_Significant_total_srs2_srr_w1<-Result_table_Significant_total_srs2_srr_w1[with(Result_table_Significant_total_srs2_srr_w1,order(FDR)),]

#######plot the data
plot_total_srs2_srr_w1_adj <- Result_table_Significant_total_srs2_srr_w1 %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "W1_total_srs2_srr-adjusted",
    color = "Pathway"
  )

plot_total_srs2_srr_w1_adj
```


6mth ASD_TOT_P

```{r}
#6mth
hold_6mth<-n_6m
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6mth)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_6mth)[i],"+ sex+ BMI6mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_6mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ASD_TOT_P_MCA1_6mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ASD_TOT_P_MCA1_6mth_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_6mth <- subset(Result_table_fdr_ASD_TOT_P_MCA1_6mth,p.value<= 0.05)#49significant

Result_table_Significant_ASD_TOT_P_MCA1_6mth<-Result_table_Significant_ASD_TOT_P_MCA1_6mth[with(Result_table_Significant_ASD_TOT_P_MCA1_6mth,order(FDR)),]


plot_ASD_TOT_P_MCA1_6mth <- Result_table_Significant_ASD_TOT_P_MCA1_6mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6mth_Metabolites-ASD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )

plot_ASD_TOT_P_6mth
```


#6mt ASD
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6mth)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_6mth)[i],"+ sex+ BMI6mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_6mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_6mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ADHD_TOT_P_MCA1_6mth_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_6mth <- subset(Result_table_fdr_IH_TOT_P_6mth,p.value<= 0.05)#49significant

Result_table_Significant_ADHD_TOT_P_MCA1_6mth<-Result_table_Significant_ADHD_TOT_P_MCA1_6mth[with(Result_table_Significant_ADHD_TOT_P_MCA1_6mth,order(FDR)),]


plot_ADHD_TOT_P_MCA1_6mth <- Result_table_Significant_ADHD_TOT_P_MCA1_6mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6mth_Metabolites-IH_TOT_P-adjusted",
    color = "Pathway"
  )

plot_ADHD_TOT_P_MCA1_6mth

```
6MTH adhdrs
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6mth)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_6mth)[i],"+ sex+ BMI6mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, a.action=na.omit,data=hold_6mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_6mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_adhdrs_6mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_adhdrs_6mth_adj.csv")

Result_table_Significant_adhdrs_6mth <- subset(Result_table_fdr_adhdrs_6mth,p.value<= 0.05)#49significant

Result_table_Significant_adhdrs_6mth<-Result_table_Significant_adhdrs_6mth[with(Result_table_Significant_adhdrs_6mth,order(FDR)),]


plot_adhdrs_6mth <- Result_table_Significant_adhdrs_6mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6mth_Metabolites-adhdrs-adjusted",
    color = "Pathway"
  )

plot_adhdrs_6mth
```
6mth srs
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6mth)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_6mth)[i],"+ sex+ BMI6mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_6mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_total_srs2_srr_6mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_total_srs2_srr_6mth_adj.csv")

Result_table_Significant_total_srs2_srr_6mth <- subset(Result_table_fdr_total_srs2_srr_6mth,p.value<= 0.05)#49significant

Result_table_Significant_total_srs2_srr_6mth<-Result_table_Significant_total_srs2_srr_6mth[with(Result_table_Significant_total_srs2_srr_6mth,order(FDR)),]


plot_total_srs2_srr_6mth <- Result_table_Significant_total_srs2_srr_6mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6mth_Metabolites-total_srs2_srr-adjusted",
    color = "Pathway"
  )

plot_total_srs2_srr_6mth
```

18mth total_srs2_srr
```{r}
#18mth
hold_18mth<-n_18m
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_18mth)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_18mth)[i],"+ sex+ BMI18mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,na.action=na.omit, data=hold_18mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_18mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_18mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_total_srs2_srr_18mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_total_srs2_srr_18mth_adj.csv")

Result_table_Significant_total_srs2_srr_18mth <- subset(Result_table_fdr_total_srs2_srr_18mth,p.value<= 0.05)#49significant

Result_table_Significant_total_srs2_srr_18mth<-Result_table_Significant_total_srs2_srr_18mth[with(Result_table_Significant_total_srs2_srr_18mth,order(FDR)),]


plot_total_srs2_srr_18mth <- Result_table_Significant_total_srs2_srr_18mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "18mth_Metabolites-total_srs2_srr-adjusted",
    color = "Pathway"
  )

plot_total_srs2_srr_18mth
```
18mth ADHD
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_18mth)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_18mth)[i],"+ sex+ BMI18mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,a.action=na.omit, data=hold_18mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_18mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_18mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_18mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ADHD_TOT_P_MCA1_18mth_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_18mth <- subset(Result_table_fdr_ADHD_TOT_P_MCA1_18mth,p.value<= 0.05)#49significant

Result_table_Significant_ADHD_TOT_P_MCA1_18mth<-Result_table_Significant_ADHD_TOT_P_MCA1_18mth[with(Result_table_Significant_ADHD_TOT_P_MCA1_18mth,order(FDR)),]


plot_ADHD_TOT_P_MCA1_18mth <- Result_table_Significant_ADHD_TOT_P_MCA1_18mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "18mth_Metabolites-ASD_TOT_P-adjusted",
    color = "Pathway"
  )

plot_ASD_TOT_P_18mth

```
18mth ASD
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_18mth)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_18mth)[i],"+ sex+ BMI18mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_18mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_18mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_18mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ASD_TOT_P_MCA1_18mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ASD_TOT_P_MCA1_18mth_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_18mth <- subset(Result_table_fdr_ASD_TOT_P_MCA1_18mth,p.value<= 0.05)#49significant

Result_table_Significant_ASD_TOT_P_MCA1_18mth<-Result_table_Significant_ASD_TOT_P_MCA1_18mth[with(Result_table_Significant_ASD_TOT_P_MCA1_18mth,order(FDR)),]


plot_ASD_TOT_P_MCA1_18mth <- Result_table_Significant_ASD_TOT_P_MCA1_18mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "18mth_Metabolites--adjusted",
    color = "Pathway"
  )

plot_ATT_TOT_P_18mth
```
18mth adhdrs_adhd_symptoms_sc_f
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_18mth)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_18mth)[i],"+ sex+ BMI18mth+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_18mth)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_18mth)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_18mth<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_adhdrs_18mth,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_adhdrs_18mth_adj.csv")

Result_table_Significant_adhdrs_18mth <- subset(Result_table_fdr_adhdrs_18mth,p.value<= 0.05)#49significant

Result_table_Significant_adhdrs_18mth<-Result_table_Significant_adhdrs_18mth[with(Result_table_Significant_adhdrs_18mth,order(FDR)),]


plot_adhdrs_18mth <- Result_table_Significant_adhdrs_18mth %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "18mth_Metabolites-adhdrs-adjusted",
    color = "Pathway"
  )

plot_adhdrs_18mth
```

6yr adhdrs_adhd_symptoms_sc_f
```{r}
hold_6yr<-n_6yr
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6yr)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_6yr)[i],"+ sex+ BMI6+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_6yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_adhdrs_6yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_adhdrs_6yr_adj.csv")

Result_table_Significant_adhdrs_6yr <- subset(Result_table_fdr_adhdrs_6yr,p.value<= 0.05)#49significant

Result_table_Significant_adhdrs_6yr<-Result_table_Significant_adhdrs_6yr[with(Result_table_Significant_adhdrs_6yr,order(FDR)),]


plot_adhdrs_6yr <- Result_table_Significant_adhdrs_6yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6yr_Metabolites-adhdrs-adjusted",
    color = "Pathway"
  )
plot_adhdrs_6yr

```

6YR ASD_TOT_P
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6yr)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_6yr)[i],"+ sex+ BMI6+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,na.action=na.omit, data=hold_6yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_6yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ASD_TOT_P_MCA1_6yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ASD_TOT_P_MCA1_6yr_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_6yr <- subset(Result_table_fdr_ASD_TOT_P_MCA1_6yr,p.value<= 0.05)#49significant

Result_table_Significant_ASD_TOT_P_MCA1_6yr<-Result_table_Significant_ASD_TOT_P_MCA1_6yr[with(Result_table_Significant_ASD_TOT_P_MCA1_6yr,order(FDR)),]


plot_ASD_TOT_P_MCA1_6yr <- Result_table_Significant_ASD_TOT_P_MCA1_6yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6yr_Metabolites-ASD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )
plot_ASD_TOT_P_6yr
```

6YR ASD
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6yr)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_6yr)[i],"+ sex+ BMI6+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_6yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))

write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_6yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ADHD_TOT_P_MCA1_6yr_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_6yr <- subset(Result_table_fdr_ADHD_TOT_P_MCA1_6yr,p.value<= 0.05)#49significant

Result_table_Significant_ADHD_TOT_P_MCA1_6yr<-Result_table_Significant_ADHD_TOT_P_MCA1_6yr[with(Result_table_Significant_ADHD_TOT_P_MCA1_6yr,order(FDR)),]


plot_ADHD_TOT_P_MCA1_6yr <- Result_table_Significant_ADHD_TOT_P_MCA1_6yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6yr_Metabolites-ADHD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )
plot_ATT_TOT_P_6yr
```
IH_TOT_P

6yr total_srs2_srr
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_6yr)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_6yr)[i],"+ sex+ BMI6+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_6yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_6yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_6yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_total_srs2_srr_6yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_total_srs2_srr_6yr_adj.csv")

Result_table_Significant_total_srs2_srr_6yr <- subset(Result_table_fdr_total_srs2_srr_6yr,p.value<= 0.05)#49significant

Result_table_Significant_total_srs2_srr_6yr<-Result_table_Significant_total_srs2_srr_6yr[with(Result_table_Significant_total_srs2_srr_6yr,order(FDR)),]

plot_total_srs2_srr_6yr<- Result_table_Significant_total_srs2_srr_6yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "6yr_Metabolites-total_srs2_srr-adjusted",
    color = "Pathway"
  )
plot_total_srs2_srr_6yr
```
10yr  ASD_TOT_P
```{r}
hold_10yr<-n_10yr
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_10yr)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_10yr)[i],"+ sex+ BMI10+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_10yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_10yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_10yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_ASD_TOT_P_MCA1_10yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ASD_TOT_P_MCA1_10yr_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_10yr <- subset(Result_table_fdr_ASD_TOT_P_MCA1_10yr,p.value<= 0.05)#49significant

Result_table_Significant_ASD_TOT_P_MCA1_10yr<-Result_table_Significant_ASD_TOT_P_MCA1_10yr[with(Result_table_Significant_ASD_TOT_P_MCA1_10yr,order(FDR)),]

plot_ASD_TOT_P_MCA1_10yr<- Result_table_Significant_ASD_TOT_P_10yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "10yr_Metabolites-ASD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )
plot_ASD_TOT_P_10yr
```
10YR "total_srs2_srr
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_10yr)))
{
  my.formula <- paste("total_srs2_srr")
  x.var <- paste(names(hold_10yr)[i],"+ sex+ BMI10+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_10yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_10yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_total_srs2_srr_10yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_total_srs2_srr_10yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_total_srs2_srr_10yr_adj.csv")

Result_table_Significant_total_srs2_srr_10yr <- subset(Result_table_fdr_total_srs2_srr_10yr,p.value<= 0.05)#49significant

Result_table_Significant_total_srs2_srr_10yr<-Result_table_Significant_total_srs2_srr_10yr[with(Result_table_Significant_total_srs2_srr_10yr,order(FDR)),]

plot_total_srs2_srr_10yr<- Result_table_Significant_total_srs2_srr_10yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "10yr_Metabolites-total_srs2_srr-adjusted",
    color = "Pathway"
  )
plot_total_srs2_srr_10yr
################################################################

```

10yr ATT_TOT_P
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_10yr)))
{
  my.formula <- paste("ADHD_TOT_P_MCA1")
  x.var <- paste(names(hold_10yr)[i],"+ sex+ BMI10+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_10yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_10yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ADHD_TOT_P_MCA1_10yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_ADHD_TOT_P_MCA1_10yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ADHD_TOT_P_MCA1_10yr_adj.csv")

Result_table_Significant_ADHD_TOT_P_MCA1_10yr <- subset(Result_table_fdr_ADHD_TOT_P_MCA1_10yr,p.value<= 0.05)#49significant

Result_table_Significant_ADHD_TOT_P_MCA1_10yr<-Result_table_Significant_ADHD_TOT_P_MCA1_10yr[with(Result_table_Significant_ADHD_TOT_P_MCA1_10yr,order(FDR)),]

plot_ADHD_TOT_P_MCA1_10yr<- Result_table_Significant_ADHD_TOT_P_MCA1_10yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "10yr_Metabolites-ADHD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )
plot_ATT_TOT_P_10yr
```
10 YR IH_TOT_P
```{r}
hold_10yr<-na.omit(n_10yr)
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_10yr)))
{
  my.formula <- paste("ASD_TOT_P_MCA1")
  x.var <- paste(names(hold_10yr)[i],"+ sex+ BMI10+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula, na.action=na.omit,data=hold_10yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_10yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_ASD_TOT_P_MCA1_10yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_ASD_TOT_P_MCA1_10yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_ASD_TOT_P_MCA1_10yr_adj.csv")

Result_table_Significant_ASD_TOT_P_MCA1_10yr <- subset(Result_table_fdr_ASD_TOT_P_MCA1_10yr,p.value<= 0.05)#49significant

Result_table_Significant_ASD_TOT_P_MCA1_10yr<-Result_table_Significant_ASD_TOT_P_MCA1_10yr[with(Result_table_Significant_ASD_TOT_P_MCA1_10yr,order(FDR)),]

plot_ASD_TOT_P_MCA1_10yr<- Result_table_Significant_ASD_TOT_P_MCA1_10yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "10yr_Metabolites-ASD_TOT_P_MCA1-adjusted",
    color = "Pathway"
  )
plot_IH_TOT_P_10yr
```
10 YR 
```{r}
Result_table<- matrix(data=NA, nrow=683, ncol=5)
colnames(Result_table) <- c("name","Estimate", "CIL","CIH",
                            "p.value")
Result_table <- as.data.frame(Result_table)
j<- 1
for (i in 21:length(names(hold_10yr)))
{
  my.formula <- paste("adhdrs_adhd_symptoms_sc_f")
  x.var <- paste(names(hold_10yr)[i],"+maternal_education_at1w+paternal_education_at1w+familyincome_at1week" )#income+m_edu+   +mother_bmi+mother_height+mother_smoking+passivesmoke1+ motherage+mother_bmi +diabetes_all
  
  my.glm.formula <- as.formula(paste0(my.formula," ~ ", x.var))
  glm_model <- lm(my.glm.formula,na.action=na.omit, data=hold_10yr)
  print(tidy(glm_model))
  Result_table[j,1] <- names(hold_10yr)[i]
  Result_table[j,2] <- round((coef(glm_model)), 2)[2]#exp
  Result_table[j,3] <- round((confint(glm_model)), 2)[2,1]#exp
  Result_table[j,4] <- round((confint(glm_model)), 2)[2,2]#
  Result_table[j,5] <- round(tidy(glm_model)$p.value,4)[2]
  j <- j+1
}
################################################################
################################################################
pathway<-all_annotation

colnames(pathway)[1]<-"name"
colnames(pathway)[2]<-"Super_pathway"
Result_table_name<-left_join(Result_table, pathway
                        %>% dplyr::select(name,CHEMICAL_NAME,Super_pathway), by ="name")##
#Result_table_name<-data.frame(Result_table_name[,c(6,1:5,7)])
names(Result_table_name)
Result_table_fdr_adhdrs_10yr<-Result_table_name%>%
  mutate(FDR= p.adjust(Result_table_name$p.value,method="fdr"))

#Result_table_fdr_neu_w24<-Result_table_fdr_neu_w24%>%filter(!grepl("X-", CHEMICAL_NAME))
write.csv(Result_table_fdr_adhdrs_10yr,file="~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/Result_table_fdr_adhdrs_10yr_adj.csv")

Result_table_Significant_adhdrs_10yr <- subset(Result_table_fdr_adhdrs_10yr,p.value<= 0.05)#49significant

Result_table_Significant_adhdrs_10yr<-Result_table_Significant_adhdrs_10yr[with(Result_table_Significant_adhdrs_10yr,order(FDR)),]

plot_adhdrs_10yr<- Result_table_Significant_IH_TOT_P_10yr %>%
  group_by(Super_pathway) %>%
  mutate(CHEMICAL_NAME = fct_reorder(CHEMICAL_NAME, p.value)) %>%
  ungroup() %>%
  ggplot(aes(x = Estimate, y = CHEMICAL_NAME, color = Super_pathway)) +
  geom_errorbar(
    aes(xmin = CIL, xmax = CIH), width = 0.2, color = "grey40"
  ) +  # Error bars first
  geom_point(size = 3) +  # Points on top
  geom_text_repel(
    aes(label = if_else(FDR<0.05, "**", if_else(p.value<0.05, "*", ""))),
    box.padding = 0.15,  # Minimally pad the text box to keep text close
    point.padding = 0.05,  # Minimize padding from the point to avoid large gaps
    size = 4, segment.color = 'grey50',
    nudge_x = 0.15,  # Carefully adjusted to ensure text is close to the error bar end; adjust based on your plot's scale
    nudge_y = 0,  # Keep y position aligned with the data point
    direction = "y"  # Encourage vertical movement over horizontal to keep text aligned and close
  ) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey50") +
  scale_color_brewer(palette = "Paired") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  ) +
  labs(
    y = "", x = "Estimate", title = "10yr_Metabolites-adhdrs-adjusted",
    color = "Pathway"
  )
plot_adhdrs_10yr
```

w24 neu_fdr_w24_adjusted
```{r}
#ADHD
adhdrs_fdr_w24_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_w24_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_w24_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_w24_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_w24_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_w24_adj.csv",row.names=1)
total_srs2_srr_w24_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_w24_adj.csv",row.names=1)

```
W1
```{r}
adhdrs_fdr_w1_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_w1_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_w1_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_w1_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_w1_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_w1_adj.csv",row.names=1)

total_srs2_srr_w1_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_w1_adj.csv",row.names=1)
```


6mth
```{r}
adhdrs_fdr_6mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_6mth_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_6mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_6mth_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_6mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_6mth_adj.csv",row.names=1)

total_srs2_srr_6mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_6mth_adj.csv",row.names=1)

```


18mth
```{r}
adhdrs_fdr_18mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_18mth_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_18mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_18mth_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_18mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_18mth_adj.csv",row.names=1)

total_srs2_srr_18mth_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_18mth_adj.csv",row.names=1)
```

6yr
```{r}
adhdrs_fdr_6yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_6yr_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_6yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_6yr_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_6yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_6yr_adj.csv",row.names=1)

total_srs2_srr_6yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_6yr_adj.csv",row.names=1)
```
10yr
```{r}
adhdrs_fdr_10yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_adhdrs_10yr_adj.csv",row.names=1)

ASD_TOT_P_MCA1_fdr_10yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ASD_TOT_P_MCA1_10yr_adj.csv",row.names=1)

ADHD_TOT_P_MCA1_10yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_ADHD_TOT_P_MCA1_10yr_adj.csv",row.names=1)

total_srs2_srr_10yr_adjusted<-read.csv("~/Library/CloudStorage/GoogleDrive-ting.wang@dbac.dk/My Drive/paper_longitudinal_metabolomics/lg/scores/Result_table_fdr_total_srs2_srr_10yr_adj.csv",row.names=1)


# List of cell names to filter
cells_to_extract <- c("X182", "X1648", "X100001950", "X100021208", "X100005389", "X100020360")#"X100021208" X100005389 "X100020360"

# Filtering each dataframe
extracted_df1 <- adhdrs_fdr_10yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df2 <- adhdrs_fdr_6yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df3 <- adhdrs_fdr_18mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df4 <- adhdrs_fdr_6mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df5 <- adhdrs_fdr_w24_adjusted %>% filter(name %in% cells_to_extract)
extracted_df6 <- adhdrs_fdr_w1_adjusted %>% filter(name %in% cells_to_extract)
combined_dataset_adhdrs<- bind_rows(
  mutate(extracted_df1, TP = "10yr"),
  mutate(extracted_df2, TP = "6yr"),
  mutate(extracted_df3, TP = "18mth"),
  mutate(extracted_df4, TP = "6mth"),
  mutate(extracted_df5, TP = "w24"),
  mutate(extracted_df6, TP = "w1")
)
logtransform <- function(x, na.rm = FALSE) (x %>% log())

combined_dataset_adhd_log<- combined_dataset_adhd %>% mutate(across(c("OR":"CIH"), logtransform))
combined_dataset_adhd_log<-combined_dataset_adhd_log%>%mutate(Group="ADHD")
# Plotting
# Adjust the width for dodging (positioning)
# Plotting
# Adjust the width for dodging (positioning)
dodge_width <- 0.5  # Adjust as needed

# Offset for text to move it further right
text_offset <- 0.4  # Adjust this value based on your data's scale
method_order <- c("w24","w1", "6mth", "18mth","6yr", "10yr" )

#NDD
extracted_df1 <-ASD_TOT_P_MCA1_fdr_10yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df2 <- ASD_TOT_P_MCA1_fdr_6yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df3 <- ASD_TOT_P_MCA1_fdr_18mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df4 <- ASD_TOT_P_MCA1_fdr_6mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df5 <- ASD_TOT_P_MCA1_fdr_w24_adjusted %>% filter(name%in% cells_to_extract)
extracted_df6 <- ASD_TOT_P_MCA1_fdr_w1_adjusted %>% filter(name %in% cells_to_extract)

combined_dataset_ASD_TOT_P_MCA1 <- bind_rows(
  mutate(extracted_df1, TP = "10yr"),
  mutate(extracted_df2, TP = "6yr"),
  mutate(extracted_df3, TP = "18mth"),
  mutate(extracted_df4, TP = "6mth"),
  mutate(extracted_df5, TP = "w24"),
   mutate(extracted_df6, TP = "w1")
)
# Plotting
# Adjust the width for dodging (positioning)
# Plotting
# Adjust the width for dodging (positioning)
dodge_width <- 0.5  # Adjust as needed

# Offset for text to move it further right
text_offset <- 0.4  # Adjust this value based on your data's scale
method_order <- c("w24", "6mth", "18mth","6yr", "10yr" )

#ADHD
extracted_df1 <- ADHD_TOT_P_MCA1_10yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df2 <- ADHD_TOT_P_MCA1_6yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df3 <- ADHD_TOT_P_MCA1_18mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df4 <- ADHD_TOT_P_MCA1_6mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df5 <- ADHD_TOT_P_MCA1_w24_adjusted %>% filter(name %in% cells_to_extract)
extracted_df6 <- ADHD_TOT_P_MCA1_w1_adjusted %>% filter(name %in% cells_to_extract)
combined_dataset_ADHD_TOT_P_MCA1<- bind_rows(
  mutate(extracted_df1, TP = "10yr"),
  mutate(extracted_df2, TP = "6yr"),
  mutate(extracted_df3, TP = "18mth"),
  mutate(extracted_df4, TP = "6mth"),
  mutate(extracted_df5, TP = "w24"),
  mutate(extracted_df6, TP = "w1")
)

#
extracted_df1 <- total_srs2_srr_10yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df2 <-total_srs2_srr_6yr_adjusted %>% filter(name %in% cells_to_extract)
extracted_df3 <- total_srs2_srr_18mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df4 <- total_srs2_srr_6mth_adjusted %>% filter(name %in% cells_to_extract)
extracted_df5 <- total_srs2_srr_w24_adjusted %>% filter(name %in% cells_to_extract)
extracted_df6 <- total_srs2_srr_w1_adjusted %>% filter(name %in% cells_to_extract)
combined_dataset_total_srs2_srr<- bind_rows(
  mutate(extracted_df1, TP = "10yr"),
  mutate(extracted_df2, TP = "6yr"),
  mutate(extracted_df3, TP = "18mth"),
  mutate(extracted_df4, TP = "6mth"),
  mutate(extracted_df5, TP = "w24"),
  mutate(extracted_df6, TP = "w1")
)
# Plotting
# Adjust the width for dodging (positioning)
# Plotting
# Adjust the width for dodging (positioning)
dodge_width <- 0.5  # Adjust as needed

# Offset for text to move it further right
text_offset <- 0.1  # Adjust this value based on your data's scale
method_order <- c("w24","w1","6mth", "18mth","6yr", "10yr" )


combined_dataset_all <- bind_rows(
  mutate(combined_dataset_total_srs2_srr, Group = "SRS-2"),
  mutate(combined_dataset_ADHD_TOT_P_MCA1, Group = "ADHD symp comp scores"),
  mutate(combined_dataset_ASD_TOT_P_MCA1, Group = "Autistic symp comp scores"),
  mutate(combined_dataset_adhdrs, Group = "ADHD-RS")
)
#combined_dataset_all<-filter(combined_dataset_all,TP!="w1")
str(combined_dataset_all)
colnames(combined_dataset_all)[5]<-"p.value"
# Plotting
# Define the desired order for TP
method_order <- c("w24", "w1", "6mth", "18mth", "6yr", "10yr")
#method_order <- c("w24", "6mth", "18mth", "6yr", "10yr")
# Convert TP to factor with the desired order
combined_dataset_all$TP <- factor(combined_dataset_all$TP, levels = method_order)

# Plotting with adjusted order of TP 折线
# Define the desired order for TP
# Plotting with adjusted order of TP and smooth lines
ggplot(combined_dataset_all, aes(x = TP, y = Estimate, color = Group, linetype = Group)) +
  geom_smooth(aes(group = interaction(CHEMICAL_NAME, Group)), method = "loess", size = 1.5) +
  geom_point(aes(group = interaction(CHEMICAL_NAME, Group)), stat = "summary", fun.y = "mean", size = 3) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  theme_bw(base_size = 17) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "right") +
  xlab("") +
  ylab("Estimate (95%CI)") +
  ggtitle(" ") +
  facet_wrap(~ CHEMICAL_NAME, scales = "free_y") +
  #scale_y_continuous(limits = c(0.3, 3.2)) + # Setting y-axis limits
  scale_color_manual(values = c("#375E97", "#A43820", "#FFBB00","#2A3132", "#763626")) + # "#2A3132", "#763626", "#90AFC5"
  guides(color = guide_legend(title = "Group"), linetype = guide_legend(title = "Group"))
############Figure 3
# Plotting with adjusted order of TP and smooth lines
significant_points <- combined_dataset_all[combined_dataset_all$p.value < 0.05, ]

#
ggplot(combined_dataset_all, aes(x = TP, y = Estimate, color = Group, linetype = Group)) +
  geom_smooth(aes(group = interaction(CHEMICAL_NAME, Group)), method = "loess", size = 1.5,linetype = "longdash") +
  geom_point(aes(group = interaction(CHEMICAL_NAME, Group)), stat = "summary", fun.y = "mean", size = 3) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  theme_bw(base_size = 17) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "right") +
  xlab("") +
  ylab("Estimate (95%CI)") +
  ggtitle(" ") +
  facet_wrap(~ CHEMICAL_NAME, scales = "free_y") +
  scale_y_continuous(limits = c(-2, 1.5)) + # Setting y-axis limits
  scale_color_manual(values = c("#375E97", "#A43820", "#FFBB00","#A6D0E6", "#355E3B")) + # Setting color palette
  guides(color = guide_legend(title = "Group"), linetype = guide_legend(title = "Group")) +
  geom_text(data = significant_points, aes(label = "*", color = Group), vjust = -0.5, size = 6) # Aligning "*" color with Group

#ADD CI

ggplot(combined_dataset_all, aes(x = TP, y = Estimate, color = Group, linetype = Group)) +
    geom_smooth(aes(group = interaction(CHEMICAL_NAME, Group)), method = "loess", size = 1.5) +
    geom_point(aes(group = interaction(CHEMICAL_NAME, Group)), stat = "summary", fun.y = "mean", size = 3) +
    geom_errorbar(aes(ymin = CIL, ymax = CIH, group = interaction(CHEMICAL_NAME, Group)), width = 0.2) +
    geom_hline(yintercept = 1, linetype = "longdash") +
    theme_bw(base_size = 17) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          legend.position = "right") +
    xlab("") +
    ylab("Odds Ratio (OR)") +
    ggtitle(" ") +
    facet_wrap(~ CHEMICAL_NAME, scales = "free_y") +
    #scale_y_continuous(limits = c(0.3, 3.2)) +
    scale_color_manual(values = c("#375E97", "#A43820", "#FFBB00","A6D0E6", "#355E3B")) +
    guides(color = guide_legend(title = "Group"), linetype = guide_legend(title = "Group"))


# Create a vector of the metabolite names you want to keep
metabolites_to_keep <- c("X182", "X100005389", "X100020360")

# Filter the dataframe to only keep rows where 'Metabolites' column matches one of the names
filtered_df <- combined_dataset_all %>%
  filter(name %in% metabolites_to_keep)
significant_points <- filtered_df[filtered_df$p.value < 0.05, ]


ggplot(filtered_df, aes(x = TP, y = Estimate, color = Group, linetype = Group)) +
  geom_smooth(aes(group = interaction(name, Group)), method = "loess", size = 1.5) +
  geom_point(aes(group = interaction(name, Group)), stat = "summary", fun.y = "mean", size = 3) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  theme_bw(base_size = 17) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "right") +
  xlab("") +
  ylab("Estimate") +
  ggtitle(" ") +
  facet_wrap(~ CHEMICAL_NAME, scales = "free_y") +
  #scale_y_continuous(limits = c(-2.5, 1)) + # Setting y-axis limits
  scale_color_manual(values = c("#375E97", "#A43820", "#FFBB00","#355E3B")) + # Setting color palette
  guides(color = guide_legend(title = "Group"), linetype = guide_legend(title = "Group")) +
  geom_text(data = significant_points, aes(label = "*", color = Group), vjust = -0.5, size = 5) # Aligning "*" color with Group

```


